### 2014-03-02 thesis/src/chapters/chapter-scalability.tex
Thesis: push unmerged change

While scalability is a widely used term, it still lacks a clear and concise definition. Over the time, there were a few attempts to define it, yet not all of them were claimed as successful \cite{Hi90} \cite{DuRoWi06}. Hence, it is necessary to clarify this term before going into further discussion. Instinctively, scalability is perceived as an ability of a system to accommodate an increasing number of elements or objects to process. In particular, we can point out different types of scalability that are affected by increased number of requests: \cite{Bo00}:
\begin{itemize}
	\item \textit{load scalability} - an ability to work without delays and unproductive resource consumption at light, moderate, or heavy loads while making good use of available resources. Factors that may hinder load scalability include: scheduling shared resource, self-expansion, inadequate exploitation of parallelism
	\item \textit{space scalability} - memory requirements do not grow to intolerable levels as the number of items system supports increases
	\item \textit{space-time scalability} - system continues to function gracefully as the number of objects it encompasses increases by orders of magnitude
	\item \textit{structural scalability} - implementation or standards do not impede the growth of the number of objects system encompasses
\end{itemize}
Although, all of the aforementioned aspects are vital for any application, our work focuses solely on the first type of scalability. The reasoning behind this is that while all of these scalability types lies in direct responsibility of an application developer, the load scalability can be additionally improved by adding additional resources to a system. This brings us to a question what kind of resources are used by an application or more appropriately in context of this dissertation: \textit{what kind of resources can we add to improve application performance?} Required resources vary from application to application. However, among the most common one we can distinguish:
\begin{itemize}
	\item CPU
	\item memory
	\item storage
	\item network bandwidth
\end{itemize}

@@

Provisioning new server is only a first step in scaling an application, it is required to configure load balancing mechanism to make use of additional node. The two important aspects that have to be consider are: load-balancing algorithms and load-balancing scalability.

>>>>

While scalability is a widely used term, it still lacks a clear and concise definition. Over the time, there were a few attempts to define it, yet not all of them were claimed as successful \cite{Hi90} \cite{DuRoWi06}. Hence, it is necessary to clarify this term before going into further discussion. Instinctively, scalability is perceived as an ability of a system to accommodate an increasing number of elements or objects to process. In particular, we can point out different types of scalability that are affected by increased number of requests: \cite{Bo00}:
\begin{itemize}
	\item \textit{load scalability} - an ability to work without delays and unproductive resource consumption at light, moderate, or heavy loads while making good use of available resources. Factors that may hinder load scalability include: scheduling shared resource, self-expansion, inadequate exploitation of parallelism
	\item \textit{space scalability} - memory requirements do not grow to intolerable levels as the number of items system supports increases
	\item \textit{space-time scalability} - system continues to function gracefully as the number of objects it encompasses increases by orders of magnitude
	\item \textit{structural scalability} - implementation or standards do not impede the growth of the number of objects system encompasses
\end{itemize}
Although, all of the aforementioned aspects are vital for any application, our work focuses solely on the first type of scalability. The reasoning behind this statement is that, while all of these scalability types lie in direct responsibility of an application developer, the load scalability can be additionally improved by adding additional resources to a system. This brings us to a question what kind of resources are used by an application or more appropriately in context of this dissertation: \textit{what kind of resources can we add to improve application performance?} Required resources varies from an application to an application. However, among the most common ones we can distinguish:
\begin{itemize}
	\item CPU
	\item memory
	\item storage
	\item network bandwidth
\end{itemize}

@@

Provisioning a new server is only the first step in scaling an application, it is required to configure load balancing mechanism to make use of additional node. Two important aspects that have to be consider are: load-balancing algorithms and load-balancing scalability.
